Validation of Visual Statistical Inference, Applied to Linear Models (supplementary materials)

### 2013-04-16 supplementary.tex
screening power curves removed from supplementary

Following six approaches have been examined to clean the data.  Table \ref{tbl:summary} displays number of subjects and there total evaluations in each screening criteria. For our paper we picked criteria six.

@@

The power curves obtained by fitting mixed model to the data for all the experiments applying different screening criteria are shown in Figure \ref{fig:power_screening_subject}. This shows how the screening criteria may affect the results. The corresponding power curves of conventional test are also shown. Notice that no mater what criteria we apply the result does not change much for experiment 2.  % Also, estimated power curve with criteria 5 for experiment 3 is above the conventional test power curve.

@@

\begin{figure}[hbtp]
   \centering
       \scalebox{0.70}{\includegraphics{power_screening_subject.pdf}}
       \caption{The subject specific power ($K=1$) estimated from mixed model for all the six screening criteria are shown. The corresponding power curves for conventional test is shown for comparison.}
       \label{fig:power_screening_subject}
\end{figure}

>>>>

Following six approaches have been examined while cleaning the data.  Table \ref{tbl:summary} displays number of subjects and their total evaluations in each screening criteria. The criteria 1 includes all the participants hence showing number of total subjects participated in the survey for all the experiments. For our paper we used criteria six to clean the data and the results presented in the paper are based on the cleaned data.

@@

%The power curves obtained by fitting mixed model to the data for all the experiments applying different screening criteria are shown in Figure \ref{fig:power_screening_subject}. This shows how the screening criteria may affect the results. The corresponding power curves of conventional test are also shown. Notice that no mater what criteria we apply the result does not change much for experiment 2.

@@

%\begin{figure}[hbtp]
%   \centering
%       \scalebox{0.70}{\includegraphics{power_screening_subject.pdf}}
%       \caption{The subject specific power ($K=1$) estimated from mixed model for all the six screening criteria are shown. The corresponding power curves for conventional test is shown for comparison.}
%       \label{fig:power_screening_subject}
%\end{figure}
